An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-27 paper/main.tex
hide author info

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{{Kanae Tsushima\inst{1}\orcidID{0000-0002-3383-3389}} \and
  {Bach-Trong Nguyen\inst{1}\orcidID{0000-0002-6342-6020}} \and
  {Robert Gl\"{u}ck\inst{2}\orcidID{0000-0001-6990-3935}} \and
  {Zhenjiang Hu\inst{3}\orcidID{0000-0002-9034-205X}}}

\authorrunning{K. Tsushima et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{National Institute of Informatics, Japan
  \email{\{k\_tsushima,bach\}@nii.ac.jp} \and
  University of Copenhagen, Denmark
  \email{glueck@di.ku.dk } \and
  Peking University, China
  \email{huzj@pku.edu.cn}}

>>>>

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%

%\author{{Kanae Tsushima\inst{1}\orcidID{0000-0002-3383-3389}} \and
%  {Bach-Trong Nguyen\inst{1}\orcidID{0000-0002-6342-6020}} \and
%  {Robert Gl\"{u}ck\inst{2}\orcidID{0000-0001-6990-3935}} \and
%  {Zhenjiang Hu\inst{3}\orcidID{0000-0002-9034-205X}}}

\author{anonymous authors}

%\authorrunning{K. Tsushima et al.}

\authorrunning{}

% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%

%\institute{National Institute of Informatics, Japan
%  \email{\{k\_tsushima,bach\}@nii.ac.jp} \and
%  University of Copenhagen, Denmark
%  \email{glueck@di.ku.dk } \and
%  Peking University, China
%  \email{huzj@pku.edu.cn}}

\institute{anonymous}
